%

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{0pt}{2pt}

\setlist[itemize]{nosep, topsep = 1pt, after=\strut, leftmargin=1em, itemsep=3pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}
\setlength{\parskip}{5pt}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

\setlength{\textfloatsep}{0.1cm}
%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
\raggedright

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\LARGE{Stefan de Lasa} \\[7.5pt]
\href{https://www.github.com/destefy/portfolio}{\raisebox{-0.05\height}\faGithub\ destefy } \ $|$ \ 
\href{https://www.linkedin.com/in/stefandelasa}{\raisebox{-0.05\height}\faLinkedin\ stefandelasa} \ $|$ \ 
\href{mailto:stefan.delasa@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ stefan.delasa@gmail.com} \ $|$ \ 
\href{tel:+6479208916}{\raisebox{-0.05\height}\faMobile \ +1(647)-920-8916} \\
\end{tabularx}

% Education
\section{Education}
% \begin{tabularx}{\linewidth}{@{}l X @{}}
University of Toronto, Bachelor of Applied Science \& Engineering - Computer Engineering \hfill{2020-2025}
\\ Seasonal GPA: 4.0 / 4.0, Cumulative GPA: 3.81 / 4.0 (Dean’s Honour List)
% \end{tabularx}
    
% Skills
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Programming Languages: &  \normalsize{C++, C, Python, MATLAB, Javascript, Typescript, React, ARM Assembly}\\
Programming Tools:  &  \normalsize{Git, VSCode, IntelliJ, Jira, Bitbucket, Jenkins, Cypress}\\  
Hardware Tools: & \normalsize{Verilog, Multisim, ModelSim, Altium, Typhoon}
\end{tabularx}

% Experience
\section{Work Experience}

%PointClickCare
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Software Engineer Intern,} \textit{PointClickCare (PCC).} & \hfill \textbf{May - Aug 2022, Toronto, ON} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    PCC creates healthcare software solutions to assist vulnerable populations with out-of-hospital care.
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}
        \raggedright{
        \item Migrated the US “Care Insights” application to Canadian markets. Configured a backend \textbf{Spring Boot} controller to determine session permissions via API calls.
        \item Used \textbf{React} and \textbf{Typescript} in a \textbf{Agile development} team to develop front-end features to ease modification of patient screening templates. Several users mentioned improved usability from this.
        \item To improve patient screening template effectiveness, I extracted session information about which end-user workflow suggestions were followed or ignored. I then sent this information to PCC’s Pendo analytics system for subsequent analysis and template refinement.}
        \item Used \textbf{Cypress} and \textbf{Kotlin} to write service/unit level tests to ensure UI and data pipeline integrity.
    \end{itemize}
    \end{minipage}
}  
\end{tabularx}

%IESO
\begin{tabularx}{\linewidth}{ @{}l r@{} }
    \textbf{Data Management Intern}, \small{\textit{Independent Electricity System Operator.}} & \hfill \textbf{Jun - Aug 2021, Toronto, ON} \\[3.75pt]
    \multicolumn{2}{@{}X@{}}{
    \raggedright{As the Crown corporation responsible for operating/directing the electricity market in Ontario, the IESO gathers and monitors data from industrial customers throughout the province.}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}
        \item Leveraged my technical knowledge to propose how \textbf{machine learning} could improve existing processes. 
        \item Highlighted benefits of \textbf{supervised learning} to detect data anomalies using IESO’s historical datasets.
        \item Worked with peers to review Meter Service Provider data, ensuring correctness of meter billing reports.
    \end{itemize}
    \end{minipage}
}
\end{tabularx}
    
\\[-10pt]

%Research Assistant
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Research Assistant,} \textit{York University.} & \hfill \textbf{Jul - Aug 2018, Toronto, ON}\\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    Permeable pavements are a promising method to control stormwater run-off. Dr. Usman Khan’s group is investigating different \textbf{ML techniques} from mobile device input to categorize different paved surfaces.
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}
        \item Conducted experiments to gather important properties of different paved surfaces.
        \item Analyzed and inputting results into a database for subsequent training by a \textbf{ML model}.
    \end{itemize}
    \end{minipage}
}
\end{tabularx}

%Projects
\section{Projects}

%messaging app
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Messaging App,} \textit{Computer Networks Class}& \hfill Nov - Dec 2022 - \href{https://www.github.com/destefy/portfolio}{Link} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    \raggedright{Used \textbf{TCP socket programming} in \textbf{C} to make a client and server program that used a system of acknowledgements to communicate. The program:}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}
        \item Let users create and join sessions, where they could broadcast messages to other users.
        \item Implemented features like private messaging, listing active users, and password-protected login.
    \end{itemize}
    \end{minipage}
} \\
\end{tabularx}

% Dr. Mario
\begin{tabularx}{\textwidth}{ @{}l r@{} }
\textbf{Dr. Mario game,} \textit{Computer Organization Class} & \hfill Jan - Apr 2022 - \href{https://youtu.be/Sxyitkk7tpI}{Video Demonstration} \\[3.75pt] 
\multicolumn{2}{@{}X@{}}{
\raggedright{I recreated the popular NES game, Dr. Mario, on a \textbf{DE1-SoC} board using \textbf{C} and the CPUlator simulator. Dr. Mario is a tetris-like game where you move falling pills to eliminate viruses.}
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[topsep = 1pt]
        \item Designed algorithms to control inputs, collisions, and game behaviour.
        \item Detected \textbf{interrupts} from a keyboard and timers.
    \end{itemize}
    \end{minipage}
}
\end{tabularx} 

% \begin{tabularx}{\linewidth}{ @{}l r@{} }
% \textbf{Radio Transceiver} & \hfill Jan - April 2022 -  \href{https://www.github.com/destefy/portfolio}{Link to Pictures} \\[3.75pt]
% \multicolumn{2}{@{}X@{}}{
% As part of my 2nd year Hardware Design class (ECE295), I worked on a team of 3 students to design, build and test two radio transceiver (transmitter + receiver) components. Specific contributions included,
% \begin{minipage}[t]{\linewidth}
%     \begin{itemize} [nosep,after=\strut, leftmargin=1em, itemsep=3pt]
%         \item Used \textbf{Altium} and \textbf{Multisim} to design the limiter, filter, mixer, and amplifier radio receiver circuits.
%         \item Demonstrated successful integration of our subcircuits into a functioning radio receiver.
%         \item Communicated the team’s design to technical and non-technical audiences through presentations
%     \end{itemize}
%     \end{minipage}
% }
% \end{tabularx}

\section{Other}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Citizenship: &  \normalsize{Canadian and American}\\
Languages:  &  \normalsize{English (Native Proficiency), French (Native Proficiency), Polish (Beginner)}\\  
\end{tabularx}


\end{document}
