\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Software Engineer Intern,} \textit{PointClickCare (PCC).} & \hfill May - Aug 2022, Toronto, ON \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
PCC creates healthcare software solutions to assist vulnerable populations with out-of-hospital care.
\begin{minipage}[t][5.6cm]{\linewidth}
    \begin{itemize}
    \item Migrated the US “Care Insights” application to Canadian markets.
        \begin{itemize}
        \item Configured a backend \textbf{Spring Boot} controller to determine session permissions via API calls. Permissions were then used across different application workflows (e.g., exposing links, etc.)
        \end{itemize}
    \item Worked in a 10 person \textbf{Agile development} team on a suite of applications for nursing facilities.
        \begin{itemize}
        \item Used \textbf{React} and \textbf{Typescript} to develop front-end features to ease creation/modification of patient screening templates. Several internal users mentioned improved usability from this work.
        \item To improve patient screening template effectiveness, I extracted session information about which end-user workflow suggestions were followed or ignored. I then sent this information to PCC’s Pendo analytics system for subsequent analysis and template refinement.
        \item Used \textbf{Cypress} and \textbf{Kotlin} to write service-level and unit tests to catch regressions and ensure front-end UI and data pipeline integrity.
        \end{itemize}
    \end{itemize}
    \end{minipage}
}  
\end{tabularx} \\